\doctitle

### 2023-05-06 pinode.tex
Remove todos

\section{Introduction}
\edit{Write a big-picture intro to machine learning for physics}
\subsection{Related Work}
\edit{Split original intro into prior works paragraphs: DL for Ph, ROMs, PIML}
\edit{Add physics-informed ML overview (PINN, DeepONet, NFO)}
        Forecasting the behavior of a large-scale real-world system directly from first principles often requires solving highly-nonlinear governing equations such as high-dimensional ordinary differential equations (ODEs) or partial differential equations (PDEs). 
        High-fidelity simulations of such dynamical systems can become intractable, especially if an online control algorithm requires multiple forecasts per second using a low-powered embedded device \cite{rowley2017model,lucia2004reduced,benner2015survey}. A situation like this arises, for example, when a smart heating, ventilation, and air conditioning (HVAC) system attempts to optimize the temperature distribution of the air in a room using only partial measurements \cite{farahmand2016learning,nabi2022robust}. At the time of writing this document, such systems are incapable of real-time complex simulations, but they can already run low-dimensional pre-trained models, which invites the development of high-quality reduced order models (ROMs) \cite{otterness2017evaluation}. Therefore, ROMs are essential for enabling the design optimization, uncertainty propagation, predictive modeling, and control for such dynamical systems \cite{brunton2022data,kutz2016dynamic,rowley2017model,jones2020characterising}

@@

        \edit{Add Koopman example to the intro}

        \edit{Add compressive sensing application to the intro}

>>>>

\section{Introduction}
\subsection{Related Work}
        Forecasting the behavior of a large-scale real-world system directly from first principles often requires solving highly-nonlinear governing equations such as high-dimensional ordinary differential equations (ODEs) or partial differential equations (PDEs). 
        High-fidelity simulations of such dynamical systems can become intractable, especially if an online control algorithm requires multiple forecasts per second using a low-powered embedded device \cite{rowley2017model,lucia2004reduced,benner2015survey}. A situation like this arises, for example, when a smart heating, ventilation, and air conditioning (HVAC) system attempts to optimize the temperature distribution of the air in a room using only partial measurements \cite{farahmand2016learning,nabi2022robust}. At the time of writing this document, such systems are incapable of real-time complex simulations, but they can already run low-dimensional pre-trained models, which invites the development of high-quality reduced order models (ROMs) \cite{otterness2017evaluation}. Therefore, ROMs are essential for enabling the design optimization, uncertainty propagation, predictive modeling, and control for such dynamical systems \cite{brunton2022data,kutz2016dynamic,rowley2017model,jones2020characterising}

@@
